Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-09-01 Journal1/Response4/Response.tex

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TNSM \\[-6ex]}
\date{}

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their constructive comments on our manuscript. They have been beneficial in revising this paper, and we have improved the technical content and presentation quality through their assistance. We greatly appreciate their generous help. We also aim for a more concise manuscript.
We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent  Comments to the Author} ``I think that the paper has improved substantially. However, to make the paper suitable for publication, the comments of reviewer 2 should be taken into account.''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the Editor for his constructive comments on how to improve our paper. Thanks to the comments, we were able to make improvements to our paper and eliminate problems. In response to the reviewers and Editor's comments, we are confident we addressed their suggestions.
We have updated the manuscript and uploaded our point-by-point response to the reviewers' comments (below).

@@

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The authors have taken into consideration all the comments and suggestions raised by the Reviewer and have provided a substantial work to improve the quality of the manuscript. In that regard the Reviewer recommends the acceptance of the paper''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is a pleasure to have the reviewer read this manuscript; we appreciate his/her attention, which helps us enhance our paper.

% % % % % % % % % % % % % % % Reviewer 2 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 2} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper addresses most comments from previous revisions. However, its organization and presentation is still too weak. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Throughout this process, we thank the reviewer for taking the time to read the manuscript carefully, commenting thoughtfully, and offering suggestions that made the manuscript stronger and more valuable. 
In this response, we hope to alleviate the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``First, the introduction is too long and does not synthesize the expectations of the rest of the paper. It must be changed to follow a the structure followed by other papers published in TNSM. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Based on this comment, we have read several TNSM papers, rewritten the introduction's paragraph, removed the additional parts, and tried to enhance it as much as possible.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} ``Second, many paragraphs are too long, what makes the path of the paper difficult to follow. For instance, paragraphs in the introduction give too much detail. Such details must be moved to the appropriate section and place a summary in the introduction. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We have rewritten the introduction and literature review section, removed the additional part, and put it in the correct sections.
We have shortened long paragraphs and sentences in this paper in order to make it easier to read.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``Regarding the technical content, the performance evaluation (Table III) must also include the related work, so that the reader knows the position of the proposed scheme in relation to dynamic resource allocation and baseline schemes. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment4:} ``Moreover, it is not clear why the fact that a function increase justifies the convergence of the algorithm. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for reporting this ambiguity. We revised this vague statement and added it to section VI-C-2. Below we reported the revised sentences.

Due to limited resources in power, the number of PRBs, and the number of activated VNFs and restrictions based on this limitation on power, energy, fronthaul capacity, etc., the objective function that is the summation of the achievable rates of UEs cannot exceed its optimal value and become infinite. Therefore, we can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations. Consequently, it converges to the optimum value.

\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 3} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper has addressed the reviewers' comments satisfactorily. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We appreciate the reviewer's time and attention in reading this manuscript.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``One minor issue is in Eq. (3) where the plus sign should be in the position after the quantization noise term. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for correcting our mistake. We modified the position of the plus sign, and the updated version is below.
\begin{align}\label{eqI}
&I_{r,u(s,i)}^{k} =\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}} + \nonumber\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{k \: H}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}},
\end{align}

\end{document}

### 2022-09-01 Journal1/paper5TNSM/pr.tex
add file

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.
The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
Consequently, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.
\end{abstract}
\begin{IEEEkeywords}
open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
\end{IEEEkeywords}
\section{Introduction}
%\subsection{State Of The Arts}
\textcolor{MidnightBlue}{Network slicing is a key technology in 5G wireless systems. Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes \cite{shen2020ai,setayesh2020joint,popovski20185g}. There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming. Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity. Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.}
%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}

\textcolor{MidnightBlue}{Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. \ref{fig:c11}, is introduced to deal with these issues.}
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.}
\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.}

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipment (UE). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service. Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient. In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost. Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges. 
One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.  }
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

\textcolor{MidnightBlue}{The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation. Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.}

@@

\textcolor{MidnightBlue}{This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.}
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.}
\item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
\item \textcolor{MidnightBlue}{We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.}
\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
\end{itemize}

@@

\begin{table}[H]
\vspace*{-0em}
 \caption {List of Acronyms} \label{table:11a}
 \vspace*{-1em}
 \begin{center}
 \scalebox{1}{
  \begin{tabular}{l  l }
  \toprule
  \vspace*{-0.3em}
\textbf{Acronym} & \textbf{Definition} \\ [0.3ex]
   \toprule
  VNF & virtual network function\\[.3ex]

  VM & virtual machine  \\[.3ex]
  RAN &  radio access network \\[.3ex]
 O-RAN & open RAN  \\[.3ex]
 vRAN & virtual RAN \\[.3ex]
 CRAN & cloud RAN \\[.3ex]
   QoS &  quality of service \\[.3ex]
  MIMO & multiple input multiple output \\[.3ex]
  PRB &  physical resource block \\[.3ex]
  SINR & signal to interference and noise ratio  \\[.3ex]
  eMBB & enhanced mobile broadBand \\[.3ex]

@@

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}
 \vspace*{-3em}
\section{Related Literature}\label{RL}
The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels. The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity. Meanwhile, the allocation of power and PRB is performed at the lower level.
In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
\textcolor{MidnightBlue}{In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.} Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

>>>>

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.
The limited fronthaul capacity and end-to-end delay constraints are simultaneously considered.
Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.
Consequently, we break it down into two different steps and propose an iterative algorithm that finds a near-optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is resolved.
The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.
\end{abstract}
\begin{IEEEkeywords}
open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.
\end{IEEEkeywords}
\section{Introduction}
%\subsection{State Of The Arts} \textcolor{MidnightBlue}{}
Network slicing is a key technology in 5G wireless systems. \textcolor{MidnightBlue}{Network slicing isolates network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving various service classes.} \cite{shen2020ai,setayesh2020joint,popovski20185g}.

There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). \textcolor{MidnightBlue}{Each service is assigned to a network slice depending on its corresponding quality of service (QoS) requirements.}
For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming. \textcolor{MidnightBlue}{Meanwhile, the URLLC service provides ultra-reliable and low-latency connectivity, e.g., for autonomous vehicles, Tactile Internet, and remote surgeries.} Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads \cite{dogra2020survey,alsenwi2021intelligent,SL}.
%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}

\textcolor{MidnightBlue}{Radio access networks (RANs) currently lack adequate flexibility and openness to handle these simultaneous service demands. Given this, a new RAN paradigm, called open RAN (O-RAN), schematically represented in Fig. \ref{fig:c11}, is introduced to deal with these issues.}
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

\textcolor{MidnightBlue}{The O-RAN architecture separates hardware and software, enabling network function virtualization (NFV).} Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG} are virtualized and implemented as VNFs.}

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The optimal resource allocation for the 5G and 6G systems is crucial to reducing costs and improving user equipment (UE). Significant challenges face these systems, including interference alignment, limited capacity of the fronthaul links, energy restrictions on VMs, etc \cite{lee2018dynamic,SystemCostMinimization}.}

\textcolor{MidnightBlue}{Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering a single service's power, data rate, and delay limitations. This architectural model is inefficient in 5G and 6G since it needs to serve services with different QoS simultaneously. Therefore, O-RAN can simultaneously support multiple services at a lower cost by being flexible, layered, and modular.  
Balancing different services with different QoS, resource requirements, and priorities is a fundamental problem \cite{ORANArch, gavrilovska2020cloud, kazemifard2021minimum, shen2020ai}.}  
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

\textcolor{MidnightBlue}{This paper aims to design an O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC, via network slicing and resource allocation.} Specifically, we intend to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.

@@

\textcolor{MidnightBlue}{This paper studies the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G services.}
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN architecture. The three types of 5G service classes, i.e., eMBB, URLLC, and mMTC, are considered in this system. We take into account their corresponding QoS requirements and service priorities.}
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. \textcolor{MidnightBlue}{Additionally, we analyze the feasibility region of the problem and introduce a fast algorithm to check it numerically.}
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}

@@

\begin{table}%[H]
\vspace*{-0em}
 \caption {List of Acronyms} \label{table:11a}
 \vspace*{-1em}
 \begin{center}
 \scalebox{1}{
  \begin{tabular}{l  l }
  \toprule
  \vspace*{-0.3em}
\textbf{Acronym} & \textbf{Definition} \\ [0.3ex]
   \toprule
  VNF & virtual network function\\[.3ex]

  VM & virtual machine  \\[.3ex]
  RAN &  radio access network \\[.3ex]
 O-RAN & open RAN  \\[.3ex]
 vRAN & virtual RAN \\[.3ex]
 CRAN & cloud RAN \\[.3ex]
  RRH & radio remote head \\[.3ex]
   BBU & baseband unit \\[.3ex]
   QoS &  quality of service \\[.3ex]
  MIMO & multiple input multiple output \\[.3ex]
  PRB &  physical resource block \\[.3ex]
  %SINR & signal to interference and noise ratio  \\[.3ex]
  eMBB & enhanced mobile broadBand \\[.3ex]

@@

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \vspace*{-2.5em}
 \end{table}
% \vspace*{-3em}
\section{Related Literature}\label{RL}
The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
\textcolor{MidnightBlue}{Two levels of dynamic network slicing in heterogeneous C-RAN (H-CRAN) are examined in \cite{lee2018dynamic}. The higher level manages user acceptance control, RRH association, and the allocation of BBU capacity. Meanwhile, PRB and power are allocated at lower levels.}
In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system and executed using deep reinforcement learning. \textcolor{MidnightBlue}{In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators.}

\textcolor{MidnightBlue}{Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent work.}
\textcolor{MidnightBlue}{
%In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to ensure eMBB and URLLC QoS requirements.
}Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
\textcolor{MidnightBlue}{In \cite{alsenwi2021intelligent}, a deep reinforcement learning algorithm is used to solve the resource allocation problem for eMBB and URLLC services.}
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

\textcolor{MidnightBlue}{In \cite{SystemCostMinimization,guo2016exploiting}, VMs activation and beamforming allocation are discussed in C-RAN systems.
Paper \cite{SystemCostMinimization} minimizes energy cost with system delay, fronthaul capacity, and rate constraints.
To guarantee UE delays, M/M/1 queueing theory is used for transmission and processing delays.}
In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.
